\begin{thebibliography}{9}
\bibitem{portutesis}
  André Pintado Jorge Gonçalves. \emph{$Sense^{2}$ A Music System based on Paintings}. Instituto Superior Técnico: Universidade Técnica de Lisboa Octubre 2009.\\
 \url{https://dspace.ist.utl.pt/bitstream/2295/570110/1/dissertacao.pdf}

 \bibitem{colorpsy}
  Andrew J. Elliot (University of Rochester), Markus A. Maier (University of Munich), Arlen C. Moller and Ron Friedman (University of Rochester), and Jörg Meinhardt (Univeristy of Munich). \emph{Color and Psychological Functioning: The Effect of Red on Performance Attainment}. Journal of Experimental Psychology: General, 2007, Vol. 136, No. 1, pp. 154 –168.

 \bibitem{DeSensuEtSensato}
 Aristóteles. \emph{De Sensu et Sensato}.

 \bibitem{BrianEnoInterview}
 \emph{Brian Eno's Thoughts On Ambient Music}. Trouser Press interview, 1982. \\
 \url{http://www.synthtopia.com/content/2009/09/17/brian-enos-thoughts-on-ambient-music/}

\bibitem{AIMusicSurvey}
 Arshia Cont. \emph{Artificial Intelligence and Music: A critical survey and proposal}. May 2005, University of California at San Diego.\\
 \url{http://cosmal.ucsd.edu/arshia/papers/AI_Music_survey.pdf}

\bibitem{VideoRedesFliparColores}
 David Eagleman. \emph{Redes: Flipar en Colores}. Emisión Redes cap 22, 9 Febrero 2009.\\
 \url{http://www.redesparalaciencia.com/249/redes/redes-22-flipar-en-colores-29-minutos}

\bibitem{bricksConvertsMusic}
 Dimitrios Margounakis, Dionysios Politis. \emph{Converting Images to Music using their Colour Properties}. Proceedings of the 12th International Conference on Auditory Display, London, UK, June 20-23, 2006.\\
 \url{http://www.dcs.qmul.ac.uk/research/imc/icad2006/proceedings/papers/f66.pdf}

\bibitem{SICOM}
 F. Pereira, C. Grilo, L. Macedo, and A. Cardoso. \emph{Composing Music with Case-Based Reasoning}. International Conference on Computational Models of Creative Cognition, Dublin, 1997.
 \url{http://iconline.ipleiria.pt/bitstream/10400.8/94/1/ICCMCC1997.pdf}

\bibitem{AIMethodsForComposition}
 G. Papadopoulos and G. Wiggins. \emph{AI Methods for Algorithmic Composition: A Survey, a Critical View  and Future Prospect}. Proceedings of the AISB’99 Symposium on Musical Creativity, Edinburgh, UK, 1999.\\
 \url{http://qmul.academia.edu/GeraintWiggins/Papers/201960/AI_Methods_for_Algorithmic_Composition_A_Survey_a_Critical_View_and_Future_Prospects}

\bibitem{pajares}
 Gonzalo Pajares, Jesús M. de la Cruz. \emph{Visión por Computador: Imágenes digitales y aplicaciones}. RA-MA, 2001.

\bibitem{micrologus}
 Guido d'Arezzo. \emph{Micrologus} (traducido al inglés por Warren Babb). 1027.

\bibitem{ScriabinQuintasColor}
 Ingrid Calvo Ivanovic. \emph{Sinestesia Cromática}.
 \url{http://www.proyectacolor.cl/significados-del-color/sinestesia-cromatica/}

\bibitem{OpticksNewton}
 Isaac Newton. \emph{Opticks}.

 \bibitem{ChaosTeoriaMusica}
Jack Sisson.\emph{Creating Music from Chaos}.12 de Junio de 2007, Math 53.\\
\url{http://www.math.dartmouth.edu/archive/m53f07/public_html/proj/Sisson.doc}

\bibitem{HistoryAlgorithmicComp}
 Jhon A. Maurer. \emph{A Brief History of Algorithmic Composition}. March, 1999.
 \url{https://ccrma.stanford.edu/~blackrse/algorithm.html}

\bibitem{GenJam}
 John Biles. \emph{GenJam: A Genetic Algorithm for Generating Jazz Solos}. 1994, pp. 131-137.\\
 \url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.55.6146}

\bibitem{AudioVisualSurvey}
 K. Giannakis and M. Smith. \emph{Imaging Soundscapes: Identifying Cognitive Associations between Auditory and Visual Dimensions}. Godoy, R. I., Jorgensen, H. (eds.): Musical Imagery, Swets \& Zeitlinger, 2001, pp. 161-179.\\
 \url{http://quod.lib.umich.edu/cgi/p/pod/dod-idx?c=icmc;idno=bbp2372.2000.167}

\bibitem{rusofotos}
Lauri Gröhn. \emph{Sound of Paintings}.\\
\url{http://www.synestesia.fi/}

\bibitem{TheUnityOfTheSenses}
 Lawrence E. Marks. \emph{The Unity Of The Senses}. 1978, pp. 93.

 \bibitem{qtlibs}
  \emph{Librerías Qt versión 4.7.4}.\\
  \url{http://qt.nokia.com/downloads}

 \bibitem{opencvDoc}
  \emph{OpenCV 2.1 C++ Reference}.\\
  \url{http://opencv.willowgarage.com/documentation/cpp/index.html}

 \bibitem{dibujosymusica}
\emph{Programa Web - Música a través de un dibujo}
\url{http://drawmusic.ksan.ru/}

 \bibitem{phononQt}
 \emph{Qt Development Network: Phonon Module}
 \url{http://qt-project.org/doc/qt-4.8/phonon-module.html}
 
 \bibitem{phononOverview}
 \emph{Qt Development Network: Phonon Overview}
 \url{http://doc.trolltech.com/4.4/phonon-overview.html}

\bibitem{SunVox}
\emph{SunVox - Multiplatform Modular Music Creation Studio}\\
\url{http://www.warmplace.ru/soft/sunvox/}

\bibitem{toneMatrix}
\emph{ToneMatrix}\\
\url{http://tonematrix.audiotool.com/}

\bibitem{Phonogramme}
 V. Lesbros. \emph{From Images to Sounds: A Dual Representation}. Computer Music Journal 20 (3), 1996, pp. 59-69.\\
 \url{http://www.jstor.org/discover/10.2307/3680824?uid=3737952&uid=2129&uid=2&uid=70&uid=4&sid=56229244313}

\bibitem{paperSyn}
  V.S. Ramachandran \& E.M. Hubbard. \emph{Synaesthesia - A Window Into Perception, Thought and Language}. Journal of Conscousness Studies, 8, No.12, 2001, pp.3-34.

\bibitem{ConcerningSpiritualArt}
 Wassily Wassilyevich Kandinsky. \emph{Concerning the Spiritual in Art}. 1911.

\bibitem{organosColor}
 William Moritz. \emph{The Dream of Color Music, and Machines that made it possible}. Animation World, Issue 2.1, April 1997,\\ 
 \url{http://www.awn.com/mag/issue2.1/articles/moritz2.1.html}

\bibitem{GestaltPsychology}
 Wolfgang Köhler. \emph{Gestalt Psychology}. Nueva York: Liveright, 1929.

\bibitem{ImageBaseComposition}
 Xiaoying Wu, Ze-Nian Li. \emph{A Study of Image-based Music Composition}. Multimedia and Expo, 2008 IEEE International Conference on.Hannover, June 23 2008-April 26 2008, pp. 1345-1348.\\
 \url{https://www.cs.sfu.ca/research/groups/VML/image_based_music/wu_icme08.pdf}
\end{thebibliography}